### 2018-05-14 Paper/examples.tex
..

In section~\ref{sec:method}, we presented a methodology for constructing
an ROS by identifying unimportant parameters based on 
estimates of the upper bound on the Sobol'
total effect sensitivity index ($\mathcal{T}(\theta_i)$) for individual parameters.
In this section, we motivate the methodology by applying it to three test problems,
namely, the borehole function, a non-linear oscillator, and a semi-linear elliptic PDE.
Since model evaluations in all these test
problems are inexpensive, we compare relative importance of model parameters based
on DGSMs, obtained using model predictions with 
converged estimates of $\mathcal{T}(\theta_i)$ based on the surrogate, constructed in the
full parameter space. Additionally, to illustrate computational gains, we compare
convergence trends as a function of training runs for the ROS and the full-space
surrogate. Furthermore, as discussed earlier in section~\ref{sec:method}, we compare
PDFs of the model output, obtained using the ROS and the full-space surrogate for
the purpose of verification.

>>>>

In section~\ref{sec:method}, we presented a framework for constructing
an ROS (if deemed advantageous) by identifying unimportant parameters based on 
estimates of the screening metric, $\widehat{\mathcal{C}_i\mu_i}$
for individual parameters.
In this section, we motivate the underlying methodology by applying it to three test problems,
namely, the borehole function, a non-linear oscillator, and a semi-linear elliptic PDE.
Since model evaluations in all these test
problems are inexpensive, we compare relative importance of model parameters based
on the screening metric, obtained using model evaluations with 
converged estimates of $\mathcal{T}(\theta_i)$ based on the surrogate constructed in the
full parameter space (FSS). Additionally, to illustrate computational gains, we compare
convergence trends as a function of training runs for the ROS and the FSS using 
$\epsilon_{\mbox{\tiny LOO}}$ in Eq.~\ref{eq:loo}. 
Furthermore, as discussed earlier in section~\ref{sec:method}, we compare
PDFs of the model output, obtained using the ROS and the full-space surrogate for
the purpose of verification.
